Vaccine data modeling: Custom MCMC solution

### 2021-03-03 notebooks/s1-model-structure-learning.Rmd
some refactoring and updated readme
before looking back

```{r}
source("vacc_import_data.R", chdir = TRUE)
```

@@

compute_scoretables <- FALSE # uncomment to recompute scoretables
source("../scripts/custom-structure-learning/fit-cog-models.R", chdir=TRUE)

@@

scoretables <- list(
  readRDS("scoretable-unconstrained.rds"),
  readRDS("scoretable-intent_is_dv.rds"),
  readRDS("scoretable-abstract_are_parents.rds"),
  readRDS("scoretable-abstract_are_parents_intent_dv.rds"),
  readRDS("scoretable-theoryBasedHierarchy.rds")
  )

# # DO MCMC - comment to skip and load saved results
# all_results <- list(list(), list(), list(), list(), list())
# 
# customize_BiDAG() # customize bidag!
# 
# for (i in 1:length(startspaces)) {
#   all_results[[i]] <- parallel_orderMCMC(train,
#                                        startspaces[[i]],
#                                        scoretables[[i]],
#                                        MAP = FALSE, # might error
#                                        1e6,
#                                        100,
#                                        blacklist = blacklists[[i]],
#                                        chains = 4,
#                                        cores = 4
#                                        )
# 
# }
# 
# reinit_BiDAG() # set it back!

# saveRDS(all_results, "allresults.rds")

>>>>

```{r}
source("../scripts/load-data-s1.R", chdir = TRUE)
```

@@

# compute_scoretables <- FALSE # uncomment or set to TRUE to recompute scoretables
source("../scripts/custom-structure-learning/fit-cog-models.R", chdir=TRUE)

## NOTE: make sure to fix to recompute all 5
```

@@

scoretables <- list(
  readRDS("../local/scoretable-unconstrained.rds"),
  readRDS("../local/scoretable-intent_is_dv.rds"),
  readRDS("../local/scoretable-abstract_are_parents.rds"),
  readRDS("../local/scoretable-abstract_are_parents_intent_dv.rds"),
  readRDS("../local/scoretable-theoryBasedHierarchy.rds")
  )

# DO MCMC - comment to skip and load saved results
all_results <- list(list(), list(), list(), list(), list())

customize_BiDAG() # customize bidag!

for (i in 1:length(startspaces)) {
  all_results[[i]] <- parallel_orderMCMC(train,
                                       # startspaces[[i]],
                                       t(startspaces[[i]]),
                                       scoretables[[i]],
                                       MAP = FALSE, # might error
                                       1e6,
                                       100,
                                       blacklist = t(blacklists[[i]]),
                                       chains = 4,
                                       cores = 4
                                       )

reinit_BiDAG() # set it back!

saveRDS(all_results, "../local/allresults.rds")
